---
title: "National Park Markers"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
This will be for using leaflet to create interactive markers for a leaflet based HTML widget. The html map will eventually be embedded on my website.

```{r, include=FALSE}
require(leaflet)
require(htmltools)
```
Read in the national park information that was previously created. 
```{r, include=FALSE}
NatParks<-read.csv("NatParks.Leaflet/National_Parks_Information.csv", stringsAsFactors = F)
head(NatParks)
```
Load up a leaflet map and add markers.
```{r, include=FALSE}
test<-leaflet(options =  leafletOptions(minZoom = 3, maxZoom = 12)) %>%
  addTiles() %>%
  addMarkers(lng = NatParks$Lon, lat = NatParks$Lat)

test
```

I need to create a set of content popups for the Nat Parks.
```{r, include=FALSE}
content <- paste("<a href=",NatParks[,7],">",NatParks[,3],"</a><br/>Size",NatParks[,5],"<br/>Visitors Pr Year",NatParks[1,4])

```


Now I want to add in popup with information about the parks
```{r, include=FALSE}
t<-leaflet(NatParks, options = leafletOptions(minZoom = 3, maxZoom = 13)) %>%
  addProviderTiles(providers$OpenTopoMap) %>%
  addMarkers(~Lon,~Lat, popup = paste("<a href=",NatParks[,7],">",NatParks[,3],"</a><br/>Size",NatParks[,5],"<br/>Visitors Pr Year",NatParks[,4])
 )
t
```
This code chunk gets at the HTML of the markers and allows for CSS styling.
```{r, echo=FALSE}
browsable(
  tagList(list(
    tags$head(
      tags$style(
        ".leaflet-popup-content-wrapper {
    background: white;
    color: black;
    padding: 1px;
    border-radius: 25px;
    }
        "
      )
    ),
    t
  ))
)

```

